---
title: "Weekly reports"
date: "9/28/2020"
author: "Young Ha Suh"
output: github_document
editor_options: 
  chunk_output_type: console
---

This document is to built to produce weekly reports on **node health**, **tag localizations**, and the script itself for Archbold Biological Station. Script will be updated as often as upstream (CTT data_tools) is updated and new features are added. We are using R linked with GitHub to download the source code, keep track of updates and changes made on both ends, and share the code with whoever is interested. The original code is from Dr. Jessica Gorzo (jessica.gorzo@celltracktech.com). 

Download all data files (GPS, node health, beep data) from https://account.celltracktech.com/

Always start the session with `git pull upstream master` in Tools > Shell to pull any chances made upstream (CTT data_tools)

# Analyze data

### Load up our functions into memory
```{r echo = FALSE}
source("functions/data_manager.R")
source("functions/node_health.R")
```


### Set up 
Infile needs to be updated based on data that has been downloaded from CTT account weekly. 
```{r}
infile <- "../data_tools/datafiles/Sep22-28/" 

#This is where you want your output to go
outpath <- "../plots/"

freq <- "1 hour" 
```





