---
title: "Weekly reports for Archbold"
date: "9/28/2020"
author: "Young Ha Suh"  
output: github_document
editor_options: 
  chunk_output_type: console
---

This document is to built to produce weekly reports on **node health**, **tag localizations**, and the script itself for Archbold Biological Station. Script will be updated as often as upstream (CTT data_tools) is updated and new features are added. We are using R linked with GitHub to download the source code, keep track of updates and changes made on both ends, and share the code with whoever is interested. The original code is from Dr. Jessica Gorzo (jessica.gorzo@celltracktech.com). 

Download all data files (GPS, node health, beep data) from https://account.celltracktech.com/

Always start the session with `git pull upstream master` in Tools > Shell to pull any chances made upstream (CTT data_tools)

FYI: API token ae45d3ab909039f9c7f48d51c1888a9864d77388ba40b28a3bf2db5c9fa18597

# Add weekly raw data

Data will need to be downloaded from the CTT account. *Need to figure out how to do this more easily because clicking download 150 x 3 times is not fun*

Put all files into their own folder in `data_tools > datafiles > [date]`

To commit all those at once, type in shell:  
   `git add .` : add all changes    
   `git commit -m "MESSAGE here"` : commit them   
   `git push origin master` : push committed changes from local to remote repository
   
May take a hot second. Refresh github page to see if data was uploaded.    


# Code for analyzing data

#### Load up our functions into memory
```{r load-functions, message = FALSE}
source("functions/data_manager.R")
source("functions/node_health.R")
library(readxl)
```


#### Set up 
Infile needs to be updated based on data that has been downloaded from CTT account weekly. Set time accordingly.
```{r setting-up, message=FALSE}
infile <- "../data_tools/datafiles/Sep22-28/" 

#This is where you want your output to go
outpath <- "../plots"

#Set frequency
freq <-"30 min"

#Set time (example)
start_time = as.POSIXct("2020-09-22 01:00:00", tz = "America/New_York")
end_time = as.POSIXct("2020-09-28 20:00:00", tz = "America/New_York")
```

#### Tags
Get a vector of tag list. Download from Nest Matrix use following. The only part that needs to be edited before getting loaded here is removing the space between Tag and ID before importing it.
```{r list-of-tags}
#Extract list of tags
list <- read_excel("tags.xlsx")

#create a left function in r
left = function (string,char) {
    substr(string,1,char)
}
list$tagid <- left(list$TagID, 8) #only the first 8 characters are read as tag ID

#list will serve as a reference to jayID - tagID

#Extract tags as vector
tags <- as.vector(list$tagid)

#Subset tags of interest if needed
#subtags <- c("33550752", "3334551E")
```

#### Merge file and extract relevant information
This takes a while to run. 
```{r merge_files, message = FALSE}
all_data <- load_data(infile) #start_time, end_time, tags
#set arguments if you choose to subset by date or tags

beep_data <- all_data[[1]]
#beep_data <- beep_data[complete.cases(beep_data), ]

health_data <- all_data[[2]]
#health_data now has a data frame of all of your node health files. 

gps_data <- all_data[[3]]
```


#### Plot data
This creates a unique ID for each combo of radio + node, summarizes node health variables for the input time interval and each unique combo of node x radio, and then expands the data frame to NA fill for missing time x ID combos based on your time interval chosen
```{r plots}
plotting_data <- summarize_health_data(health_data, freq)
summarized <- plotting_data[[1]]
ids <- unique(summarized$ID)

# this creates a nested list of diagnostic plots for each combo of node and radio ID. You can index the list by the vector of node x ID combos passed to it
radionode_plots <- node_channel_plots(health_data, freq, ids)

# for instance radionode_plots[[1]] corresponds to the plots for ids[1]

### Examples
# work on plots
formatted <- lapply(radionode_plots, function(x) lapply(x, function(y) y + theme(axis.text=element_text(size=10),axis.title=element_text(size=30,face="bold"))))

#change 1 plot in the list (e.g. all of the batt plots)
batt_mod <- lapply(radionode_plots, function(x) {
  x[[1]] <- x[[1]] + theme(axis.text=element_text(size=10),axis.title=element_text(size=30,face="bold"))
  return(x)})

#PLOT INDICES
#1. RSSI scatter plot
#2. Battery
#3. number of check-ins
#4. check-ins as scaled line overlay of scaled RSSI plot


## if you want to write out plot images...
#call the function "export_node_channel_plots(health,outpath,x,y,z)" replacing x, y, z with the integer index of the plot desired for each of the 3 panels
#the resulting plots will be in "outpath" named "node_<RadioId>_<NodeId>.png"
export_node_channel_plots(health=health_data,freq=freq,out_path=outpath,x=4,y=2,z=1)

```

## Node health
For v2 nodes only
```{r}
health_df <- health_data[[1]]
nodes <- unique(health_df$NodeId)
#produces a list of plots per node showing if/when time stamp on sending vs. receiving mismatches occur, and if there are NA values
#you can index the list by the vector of nodes passed to it

mynodes <- node_plots(health_data,nodes,freq)
mynodes[[1]]
#90649225 is min time diff to get to 2017
#for instance mynodes[[1]] corresponds to the plots for nodes[1]

#PLOT INDICES
#1. time mismatches (i.e. indicates when a GPS fix was likely lost)
#2. smaller time delays

#call the export_node_plots() function to output the plots looking for time stamp mismatches
#the resulting plots will be in "outpath" named "nodes_<node>.png"
export_node_plots(health = health_data, freq = freq, outpath = "../plots", x = 5,y = 4, z = 1)
```


## Localization

#### Load libraries and functions
```{r load-local-functions, message = FALSE}
library(raster)
library(sp)
library(rgdal)
library(sf)
library(ggplot2)
library(geosphere)
source("functions/data_manager.R")
source("functions/localization.R")
```

#### Set up
```{r}
beep_data <- all_data[[1]][[1]]

nodes <- read.csv("../data_tools/nodes.csv") #uppercase node letters


beep_data <- beep_data[beep_data$NodeId %in% toupper(nodes$NodeId),] #c("326317", "326584", "3282fa", "3285ae", "3288f4")

```

