---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Libraries
```{r}
library(sp)
library(adehabitatHR)
library(ggplot2)
library(ggmap)
```

#Load data
Focus on channel 2

*R being dumb and can't read it all of a sudden without the path*

30 second averages for Dec 10-11
```{r}
#tags
t1 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61335578_channel_2_freq_30S.csv") 
t2 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61664C61_channel_2_freq_30S.csv") 
t3<- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_6133331E_channel_2_freq_30S.csv") 
t4 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61336634_channel_2_freq_30S.csv") 
t5 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61526633_channel_2_freq_30S.csv")
t6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_6166194C_channel_2_freq_30S.csv") 
t7 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_6134074B_channel_2_freq_30S.csv") 
t8 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61611E2D_channel_2_freq_30S.csv") 
t9 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_61664B1E_channel_2_freq_30S.csv") 
t10 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/testtags/tag_6166194B_channel_2_freq_30S.csv") 


t1$ID <- "61335578"
t1$time <- as.POSIXct(t1$Time)

t2$ID <- "61664C61"
t2$time <- as.POSIXct(t2$Time)

t3$ID <- "6133331E"
t3$time <- as.POSIXct(t3$Time)

t4$ID <- "61336634"
t4$time <- as.POSIXct(t4$Time)

t5$ID <- "61526633"
t5$time <- as.POSIXct(t5$Time)

t6$ID <- "6166194C"
t6$time <- as.POSIXct(t6$Time)

t8$ID <- "6134074B"
t8$time <- as.POSIXct(t8$Time)

t7$ID <- "61611E2D"
t7$time <- as.POSIXct(t7$Time)

t9$ID <- "61664B1E"
t9$time <- as.POSIXct(t9$Time)

t10$ID <- "6166194B"
t10$time <- as.POSIXct(t10$Time)

tags <- rbind(t1, t2, t3, t4, t5, t6, t7, t8, t9, t10)


#by platforms

platform1 <- rbind(t1,t8,t2,t7)
platform2 <- rbind(t3,t4,t5,t6)
still <- rbind(t9, t10)
```

#Get base map
```{r}
#need Google API key
register_google(key = "AIzaSyBw0JWISXhUFty3EIykKthrDrlXOPY5O_I")

mybasemap <- get_map(location = c(lon = mean(exp1.sp@coords[,1]) , 
                                  lat = mean(exp1.sp@coords[,2])), 
                     source = "google", zoom = 17, maptype = 'satellite')

ggmap(mybasemap)
```

#Node map
```{r}
#nodes
nodes <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/archbold-nodes.csv")

node_4C6 <- nodes[(nodes$NodeId == "4C6"),]
node_42A<- nodes[(nodes$NodeId == "42A"),]
node_C0 <- nodes[(nodes$NodeId == "C0"),]
node_B8 <- nodes[(nodes$NodeId == "B8"),]

node_4C6.sp <- node_4C6[c("NodeId", "lat", "lng")]
coordinates(node_4C6.sp) <- c("lng", "lat")
node_42A.sp <- node_42A[c("NodeId", "lat", "lng")]
coordinates(node_42A.sp) <- c("lng", "lat")
node_C0.sp <- node_C0[c("NodeId", "lat", "lng")]
coordinates(node_C0.sp) <- c("lng", "lat")
node_B8.sp <- node_C0[c("NodeId", "lat", "lng")]
coordinates(node_B8.sp) <- c("lng", "lat")
```

#Actual locations of platforms
```{r}
library(geosphere)

#actual location for node 4C6
act.loc.4c6 <- destPoint(node_4C6.sp, b=190, d=1.96)
act.loc.4c6.sp <- as.data.frame(act.loc.4c6)
coordinates(act.loc.4c6.sp) <- c("lon", "lat")

#actual location for node 42A
act.loc.42a <- destPoint(node_42A.sp, b=172, d=2.32)
act.loc.42a.sp <- as.data.frame(act.loc.42a)
coordinates(act.loc.42a.sp) <- c("lon", "lat")

#actual location for node B8
act.loc.b8 <- destPoint(node_B8.sp, b=103, d=3.83)
act.loc.b8.sp <- as.data.frame(act.loc.b8)
coordinates(act.loc.b8.sp) <- c("lon", "lat")

#actual location for node B8
act.loc.c0 <- destPoint(node_C0.sp, b=204, d=1.55)
act.loc.c0.sp <- as.data.frame(act.loc.c0)
coordinates(act.loc.c0.sp) <- c("lon", "lat")

```


#Filter by time
1. Platform 1 @ Node 4C6, Dec 10
exp1: ground -- horizontal 10:01-10:16
exp3: medium -- horizontal 10:17-10:32
exp5: high -- horizontal 11:42-11:57
exp7: high -- vertical 12:00-12:19
exp9: medium -- vertical 10:40-10:55 
exp11: ground -- vertical 12:20-12:35 

```{r}
exp1 <- platform1[with(platform1, time >="2019-12-10 15:01:00" & time <="2019-12-10 15:16:00"),] 
exp3 <- platform1[with(platform1, time >="2019-12-10 15:17:00" & time <="2019-12-10 15:32:00"),] 
exp5 <- platform1[with(platform1, time >="2019-12-10 16:42:00" & time <="2019-12-10 16:57:00"),]
exp7 <- platform1[with(platform1, time >="2019-12-10 17:00:00" & time <="2019-12-10 17:19:00"),]
exp9 <- platform1[with(platform1, time >="2019-12-10 15:40:00" & time <="2019-12-10 15:55:00"),]
exp11 <- platform1[with(platform1, time >="2019-12-10 17:20:00" & time <="2019-12-10 17:35:00"),]

exps.p1.4c6 <- list(exp1, exp3, exp5, exp7, exp9, exp11)
```

2. Platform 1 @ Node 42A, Dec 10
```{r}
exp17 <- platform1[with(platform1, time >="2019-12-10 18:51:00" & time <="2019-12-10 19:06:00"),] 
exp19 <- platform1[with(platform1, time >="2019-12-10 19:09:00" & time <="2019-12-10 19:24:00"),] 
exp22 <- platform1[with(platform1, time >="2019-12-10 19:49:00" & time <="2019-12-10 20:04:00"),]
exp24 <- platform1[with(platform1, time >="2019-12-10 19:30:00" & time <="2019-12-10 19:45:00"),]
exp27 <- platform1[with(platform1, time >="2019-12-10 20:07:00" & time <="2019-12-10 20:23:00"),]
exp29 <- platform1[with(platform1, time >="2019-12-10 20:31:00" & time <="2019-12-10 20:46:00"),]

exps.p1.42a <- list(exp17, exp19, exp22, exp24, exp27, exp29)
```

3. Platform 1 @ Node B8, Dec 11
```{r}
exp32 <- platform1[with(platform1, time >="2019-12-11 13:59:00" & time <="2019-12-11 14:14:00"),] 
exp34 <- platform1[with(platform1, time >="2019-12-11 14:17:00" & time <="2019-12-11 14:32:00"),] 
exp37 <- platform1[with(platform1, time >="2019-12-11 15:13:00" & time <="2019-12-11 15:28:00"),]
exp39 <- platform1[with(platform1, time >="2019-12-11 15:32:00" & time <="2019-12-11 15:47:00"),]
exp42 <- platform1[with(platform1, time >="2019-12-11 14:55:00" & time <="2019-12-11 15:10:00"),]
exp44 <- platform1[with(platform1, time >="2019-12-11 14:37:00" & time <="2019-12-11 14:52:00"),]

exps.p1.b8 <- list(exp32, exp34, exp37, exp39, exp42, exp44)
```

4. Platform 1 @ Node C0, Dec 11
```{r}
exp48 <- platform1[with(platform1, time >="2019-12-11 16:01:00" & time <="2019-12-11 16:16:00"),] 
exp50 <- platform1[with(platform1, time >="2019-12-11 17:36:00" & time <="2019-12-11 17:51:00"),] 
exp53 <- platform1[with(platform1, time >="2019-12-11 16:18:00" & time <="2019-12-11 16:33:00"),]
exp55 <- platform1[with(platform1, time >="2019-12-11 16:36:00" & time <="2019-12-11 16:51:00"),]
exp58 <- platform1[with(platform1, time >="2019-12-11 17:12:00" & time <="2019-12-11 17:27:00"),]
exp60 <- platform1[with(platform1, time >="2019-12-11 16:55:00" & time <="2019-12-11 17:10:00"),]

exps.p1.c0 <- list(exp48, exp50, exp53, exp55, exp58, exp60)
```

5. Platform 2 @ Node 4C6, Dec 10
```{r}
exp2 <- platform2[with(platform2, time >="2019-12-10 15:01:00" & time <="2019-12-10 15:16:00"),] 
exp4 <- platform2[with(platform2, time >="2019-12-10 15:17:00" & time <="2019-12-10 15:32:00"),] 
exp6 <- platform2[with(platform2, time >="2019-12-10 16:42:00" & time <="2019-12-10 16:57:00"),]
exp8 <- platform2[with(platform2, time >="2019-12-10 16:03:00" & time <="2019-12-10 16:18:00"),]
exp10 <- platform2[with(platform2, time >="2019-12-10 15:40:00" & time <="2019-12-10 15:55:00"),]
exp12 <- platform2[with(platform2, time >="2019-12-10 17:04:00" & time <="2019-12-10 17:19:00"),]

exps.p2.4c6 <- list(exp2, exp4, exp6, exp8, exp10, exp12)
```

6. Platform 2 @ Node 42A, Dec 10
```{r}
exp18 <- platform2[with(platform2, time >="2019-12-10 18:51:00" & time <="2019-12-10 19:06:00"),] 
exp20 <- platform2[with(platform2, time >="2019-12-10 19:09:00" & time <="2019-12-10 19:24:00"),] 
exp23 <- platform2[with(platform2, time >="2019-12-10 19:49:00" & time <="2019-12-10 20:04:00"),]
exp25 <- platform2[with(platform2, time >="2019-12-10 19:30:00" & time <="2019-12-10 19:45:00"),]
exp28 <- platform2[with(platform2, time >="2019-12-10 19:07:00" & time <="2019-12-10 19:23:00"),]
exp30 <- platform2[with(platform2, time >="2019-12-10 20:31:00" & time <="2019-12-10 20:46:00"),]

exps.p2.42a <- list(exp18, exp20, exp23, exp25, exp28, exp30)
```

7. Platform 2 @ Node B8, Dec 11
```{r}
exp33 <- platform2[with(platform2, time >="2019-12-11 13:59:00" & time <="2019-12-11 14:14:00"),] 
exp35 <- platform2[with(platform2, time >="2019-12-11 14:17:00" & time <="2019-12-11 14:32:00"),] 
exp38 <- platform2[with(platform2, time >="2019-12-11 15:13:00" & time <="2019-12-11 15:28:00"),]
exp40 <- platform2[with(platform2, time >="2019-12-11 15:32:00" & time <="2019-12-11 15:47:00"),]
exp43 <- platform2[with(platform2, time >="2019-12-11 14:55:00" & time <="2019-12-11 15:10:00"),]
exp45 <- platform2[with(platform2, time >="2019-12-11 14:37:00" & time <="2019-12-11 14:52:00"),]

exps.p2.b8 <- list(exp33, exp35, exp38, exp40, exp43, exp45)
```

8. Platform 2 @ Node C0, Dec 11
```{r}
exp49 <- platform2[with(platform2, time >="2019-12-11 16:01:00" & time <="2019-12-11 16:16:00"),] 
exp51 <- platform2[with(platform2, time >="2019-12-11 17:36:00" & time <="2019-12-11 17:51:00"),] 
exp54 <- platform2[with(platform2, time >="2019-12-11 16:18:00" & time <="2019-12-11 16:33:00"),]
exp56 <- platform2[with(platform2, time >="2019-12-11 16:36:00" & time <="2019-12-11 16:51:00"),]
exp59 <- platform2[with(platform2, time >="2019-12-11 17:12:00" & time <="2019-12-11 17:27:00"),]
exp61 <- platform2[with(platform2, time >="2019-12-11 16:55:00" & time <="2019-12-11 17:10:00"),]

exps.p2.c0 <- list(exp49, exp51, exp54, exp56, exp59, exp61)
```

9. Still -- Dec 10
```{r}
#node 4C6
exp13 <- still[with(still, time >="2019-12-10 16:23:00" & time <="2019-12-10 16:38:00"),] 
exp14 <- still[with(still, time >="2019-12-10 16:42:00" & time <="2019-12-10 16:57:00"),] 
exp15 <- still[with(still, time >="2019-12-10 15:01:00" & time <="2019-12-10 16:18:00"),]

exps.still.4c6 <- list(exp13, exp14, exp15)

#node 42A
exp16 <- still[with(still, time >="2019-12-10 18:51:00" & time <="2019-12-10 19:06:00"),] 
exp21 <- still[with(still, time >="2019-12-10 19:30:00" & time <="2019-12-10 19:45:00"),] 
exp26 <- still[with(still, time >="2019-12-10 20:31:00" & time <="2019-12-10 20:46:00"),]

exps.still.42a <- list(exp16, exp21, exp26)
```

10. Still -- Dec 11
```{r}
#node B8
exp31 <- still[with(still, time >="2019-12-11 13:50:00" & time <="2019-12-11 14:14:00"),] 
exp36 <- still[with(still, time >="2019-12-11 15:32:00" & time <="2019-12-11 15:47:00"),] 
exp41 <- still[with(still, time >="2019-12-11 14:37:00" & time <="2019-12-11 14:52:00"),]

exps.still.b8 <- list(exp31, exp36, exp41)

#node C0
exp47 <- still[with(still, time >="2019-12-11 16:01:00" & time <="2019-12-11 16:16:00"),] 
exp52 <- still[with(still, time >="2019-12-11 16:18:00" & time <="2019-12-11 16:33:00"),] 
exp57 <- still[with(still, time >="2019-12-11 16:55:00" & time <="2019-12-11 17:10:00"),]

exps.still.c0 <- list(exp47, exp52, exp57)

```



#Convert to spatial
```{r}
####exp1####
exp1.sp <- exp1[c("ID", "lat", "lng")]
coordinates(exp1.sp) <- c("lng", "lat")
plot(exp1.sp) 


#plot by color
exp1.sp@data$ID <- as.factor(exp1.sp@data$ID)
plot(exp1.sp, col = exp1.sp@data$ID, pch = 16) 

#MCP
exp1.mcp <- mcp(exp1.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp1.mcp

```

#Plot
```{r}
#turn spatial data frame to regular data frame to plot in ggmap
exp1.geo <- data.frame(id = exp1.sp@data$ID, # add individual identifier
                            exp1.sp@coords)
exp1.map <-ggmap(mybasemap) + 
  geom_point(data = exp1.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp1.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - ground - horizontal")

exp1.map

ggsave("exp1.png", plot = exp1.map, width=150, height=150, units="mm", dpi=300)

```


#exp3
```{r}
exp3.sp <- exp3[c("ID", "lat", "lng")]
coordinates(exp3.sp) <- c("lng", "lat")

#MCP
exp3.mcp <- mcp(exp3.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp3.mcp

exp3.geo <- data.frame(id = exp3.sp@data$ID, # add individual identifier
                            exp3.sp@coords)

exp3.map <-ggmap(mybasemap) + 
  geom_point(data = exp3.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp3.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - medium - horizontal")

exp3.map

ggsave("exp3.png", plot = exp3.map, width=150, height=150, units="mm", dpi=300)
```

#exp5
```{r}
exp5.sp <- exp5[c("ID", "lat", "lng")]
coordinates(exp5.sp) <- c("lng", "lat")

#MCP
exp5.mcp <- mcp(exp5.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp5.mcp

exp5.geo <- data.frame(id = exp5.sp@data$ID, # add individual identifier
                            exp5.sp@coords)

exp5.map <-ggmap(mybasemap) + 
  geom_point(data = exp5.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp5.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - high - horizontal")

exp5.map

ggsave("exp5.png", plot = exp5.map, width=150, height=150, units="mm", dpi=300)
```


#exp7
```{r}
exp7.sp <- exp7[c("ID", "lat", "lng")]
coordinates(exp7.sp) <- c("lng", "lat")

#MCP
exp7.mcp <- mcp(exp7.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp7.mcp

exp7.geo <- data.frame(id = exp7.sp@data$ID, # add individual identifier
                            exp7.sp@coords)

proj4string(exp7.mcp) <- CRS( "+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83" )

exp7.map <-ggmap(mybasemap) + 
  geom_point(data = exp7.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp7.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - high - vertical")

exp7.map

ggsave("exp7.png", plot = exp7.map, width=150, height=150, units="mm", dpi=300)
```

#exp9
```{r}
exp9.sp <- exp9[c("ID", "lat", "lng")]
coordinates(exp9.sp) <- c("lng", "lat")

#MCP
exp9.mcp <- mcp(exp9.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp9.mcp

exp9.geo <- data.frame(id = exp9.sp@data$ID, # add individual identifier
                            exp9.sp@coords)

exp9.map <-ggmap(mybasemap) + 
  geom_point(data = exp9.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp9.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - medium - vertical")

exp9.map

ggsave("exp9.png", plot = exp9.map, width=150, height=150, units="mm", dpi=300)
```

#exp11
```{r}
exp11.sp <- exp11[c("ID", "lat", "lng")]
coordinates(exp11.sp) <- c("lng", "lat")

#MCP
exp11.mcp <- mcp(exp11.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp11.mcp

exp11.geo <- data.frame(id = exp11.sp@data$ID, # add individual identifier
                            exp11.sp@coords)

exp11.map <-ggmap(mybasemap) + 
  geom_point(data = exp11.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp11.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - low - vertical")

exp11.map

ggsave("exp11.png", plot = exp11.map, width=150, height=150, units="mm", dpi=300)
```


##########
Need new basemap
##########

#exp17
```{r}
exp17.sp <- exp17[c("ID", "lat", "lng")]
coordinates(exp17.sp) <- c("lng", "lat")

#new basemap
mybasemap_exp17 <- get_map(location = c(lon = mean(exp17.sp@coords[,1]) , 
                                  lat = mean(exp17.sp@coords[,2])), 
                     source = "google", zoom = 17, maptype = 'satellite')

#MCP
exp17.mcp <- mcp(exp17.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp17.mcp

exp17.geo <- data.frame(id = exp17.sp@data$ID, # add individual identifier
                            exp17.sp@coords)

exp17.map <-ggmap(mybasemap_exp17) + 
  geom_point(data = exp17.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp17.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_42A, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.356, y=27.1962, label = "42A: platform 1 - ground - horizontal")

exp17.map

ggsave("exp17.png", plot = exp17.map, width=150, height=150, units="mm", dpi=300)
```

#exp19
```{r}
exp19.sp <- exp19[c("ID", "lat", "lng")]
coordinates(exp19.sp) <- c("lng", "lat")

#MCP
exp19.mcp <- mcp(exp19.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp19.mcp

exp19.geo <- data.frame(id = exp19.sp@data$ID, # add individual identifier
                            exp19.sp@coords)

exp19.map <-ggmap(mybasemap_exp17) + 
  geom_point(data = exp19.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp19.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_42A, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.356, y=27.1962, label = "42A: platform 1 - ground - vertical")

exp19.map

ggsave("exp19.png", plot = exp19.map, width=150, height=150, units="mm", dpi=300)
```

#exp22
```{r}
exp22.sp <- exp22[c("ID", "lat", "lng")]
coordinates(exp22.sp) <- c("lng", "lat")

#MCP
exp22.mcp <- mcp(exp22.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp22.mcp

exp22.geo <- data.frame(id = exp22.sp@data$ID, # add individual identifier
                            exp22.sp@coords)

exp22.map <-ggmap(mybasemap_exp17) + 
  geom_point(data = exp22.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp22.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_42A, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.356, y=27.1962, label = "42A: platform 1 - medium - horizontal")

exp22.map

ggsave("exp22.png", plot = exp22.map, width=150, height=150, units="mm", dpi=300)
```



###########
Platform 2
###########
#exp2
```{r}
exp2.sp <- exp2[c("ID", "lat", "lng")]
coordinates(exp2.sp) <- c("lng", "lat")

#MCP
exp2.mcp <- mcp(exp2.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp2.mcp

exp2.geo <- data.frame(id = exp2.sp@data$ID, # add individual identifier
                            exp2.sp@coords)

exp2.map <-ggmap(mybasemap_exp6) + 
  geom_point(data = exp2.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp2.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.20, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  theme(axis.text=element_text(size=14, color="black"),
        axis.title=element_text(size=14,face="bold",color="black"),
        axis.text.x=element_text(color="black"), 
        axis.text.y=element_text(color="black"))+
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 2 - ground - horizontal", col = "white")

exp2.map

ggsave("exp2.png", plot = exp2.map, width=150, height=150, units="mm", dpi=300)
```

#exp4
```{r}
exp4.sp <- exp4[c("ID", "lat", "lng")]
coordinates(exp4.sp) <- c("lng", "lat")

#MCP
exp4.mcp <- mcp(exp4.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp4.mcp

exp4.geo <- data.frame(id = exp4.sp@data$ID, # add individual identifier
                            exp4.sp@coords)

exp4.map <-ggmap(mybasemap_exp6) + 
  geom_point(data = exp4.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp4.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.20, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
    theme(axis.text=element_text(size=14, color="black"),
        axis.title=element_text(size=14,face="bold",color="black"),
        axis.text.x=element_text(color="black"), 
        axis.text.y=element_text(color="black"))+
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 2 - medium - horizontal", col = "white")

exp4.map

ggsave("exp4.png", plot = exp4.map, width=150, height=150, units="mm", dpi=300)
```

#exp6
```{r}
exp6.sp <- exp6[c("ID", "lat", "lng")]
coordinates(exp6.sp) <- c("lng", "lat")


mybasemap_exp6 <- get_map(location = c(lon = mean(exp6.sp@coords[,1]) , 
                                  lat = mean(exp6.sp@coords[,2])), 
                     source = "google", zoom = 17, maptype = 'satellite')

#MCP
exp6.mcp <- mcp(exp6.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp6.mcp

exp6.geo <- data.frame(id = exp6.sp@data$ID, # add individual identifier
                            exp6.sp@coords)

exp6.map <-ggmap(mybasemap_exp6) + 
  geom_point(data = exp6.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp6.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.20, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
    theme(axis.text=element_text(size=14, color="black"),
        axis.title=element_text(size=14,face="bold",color="black"),
        axis.text.x=element_text(color="black"), 
        axis.text.y=element_text(color="black"))+
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 2 - high - horizontal", col = "white")

exp6.map

ggsave("exp6.png", plot = exp6.map, width=150, height=150, units="mm", dpi=300)
```

#exp8
```{r}
exp8.sp <- exp8[c("ID", "lat", "lng")]
coordinates(exp8.sp) <- c("lng", "lat")


mybasemap_exp8 <- get_map(location = c(lon = mean(exp6.sp@coords[,1]) , 
                                  lat = mean(exp6.sp@coords[,2])), 
                     source = "google", zoom = 17, maptype = 'satellite')

#MCP
exp8.mcp <- mcp(exp8.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp8.mcp

exp8.geo <- data.frame(id = exp8.sp@data$ID, # add individual identifier
                            exp8.sp@coords)

exp8.map <-ggmap(mybasemap_exp8) + 
  geom_point(data = exp8.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp8.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "green", "yellow")) +
  scale_fill_manual(values = c("blue", "red", "green", "yellow"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 2 - high - vertical")

exp8.map

ggsave("exp8.png", plot = exp8.map, width=150, height=150, units="mm", dpi=300)
```


##############
#Summary stats
```{r}
library(raster)

#MCP size
exp1.mcp@data$area
exp1.mcp

#MCP centroid
library(rgeos)
library(Rmisc)

exp1.mcp.cent <- gCentroid(exp1.mcp)
exp1.mcp.cent

summarySE(exp1, measurevar = "lat", groupvars = "ID")
summarySE(exp1, measurevar = "lng", groupvars = "ID")


#Distance between
exp1.dist <- pointDistance(exp1.sp, act.loc.4c6.sp, lonlat = T) 
View(exp1.dist) #in meters
mean(exp1.dist) #74.81059
range(exp1.dist) #1.959825~220.878009

exp1.dist.cent <- pointDistance(exp1.mcp.cent, act.loc.4c6.sp, lonlat=T)
View(exp1.dist.cent)

exp1.dist.df <- as.data.frame(exp1.dist)
exp1.dist.df$TagID <- exp1$ID
View(exp1.dist.df)



summarySE(exp1.dist.df, measurevar = "exp1.dist", groupvars = "TagID", na.rm = T)
```






############################
############################
Remove node 4C6
############################
############################

```{r}
t1_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61335578_channel_2_freq_30S_4c6.csv") 
t2_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61664C61_channel_2_freq_30S_4c6.csv") 
t3_4c6<- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_6133331E_channel_2_freq_30S_4c6.csv") 
t4_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61336634_channel_2_freq_30S_4c6.csv") 
t5_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61526633_channel_2_freq_30S_4c6.csv")
t6_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_6166194C_channel_2_freq_30S_4c6.csv") 
t7_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_6134074B_channel_2_freq_30S_4c6.csv") 
t8_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61611E2D_channel_2_freq_30S_4c6.csv") 
t9_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_61664B1E_channel_2_freq_30S_4c6.csv") 
t10_4c6 <- read.csv("C:/Users/young/Documents/MS cell track methods/CTTMethods/node4c6/tag_6166194B_channel_2_freq_30S_4c6.csv") 

t1_4c6$ID <- "61335578"
t1_4c6$time <- as.POSIXct(t1_4c6$Time)

t2_4c6$ID <- "61664C61"
t2_4c6$time <- as.POSIXct(t2_4c6$Time)

t3_4c6$ID <- "6133331E"
t3_4c6$time <- as.POSIXct(t3_4c6$Time)

t4_4c6$ID <- "61336634"
t4_4c6$time <- as.POSIXct(t4_4c6$Time)

t5_4c6$ID <- "61526633"
t5_4c6$time <- as.POSIXct(t5_4c6$Time)

t6_4c6$ID <- "6166194C"
t6_4c6$time <- as.POSIXct(t6_4c6$Time)

t8_4c6$ID <- "6134074B"
t8_4c6$time <- as.POSIXct(t8_4c6$Time)

t7_4c6$ID <- "61611E2D"
t7_4c6$time <- as.POSIXct(t7_4c6$Time)

t9_4c6$ID <- "61664B1E"
t9_4c6$time <- as.POSIXct(t9_4c6$Time)

t10_4c6$ID <- "6166194B"
t10_4c6$time <- as.POSIXct(t10_4c6$Time)
```

```{r}
platform1_4c6 <- rbind(t1_4c6,t8_4c6,t2_4c6,t7_4c6)


exp1_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 15:01:00" & time <="2019-12-10 15:16:00"),] 
exp3_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 15:17:00" & time <="2019-12-10 15:32:00"),] 
exp5_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 16:42:00" & time <="2019-12-10 16:57:00"),]
exp7_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 17:00:00" & time <="2019-12-10 17:19:00"),]
exp9_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 15:40:00" & time <="2019-12-10 15:55:00"),]
exp11_4c6 <- platform1_4c6[with(platform1_4c6, time >="2019-12-10 17:20:00" & time <="2019-12-10 17:35:00"),]
```

```{r}
####exp1####
exp1_4c6.sp <- exp1_4c6[c("ID", "lat", "lng")]
coordinates(exp1_4c6.sp) <- c("lng", "lat")
plot(exp1_4c6.sp)

#plot by color
exp1_4c6.sp@data$ID <- as.factor(exp1_4c6.sp@data$ID)
plot(exp1_4c6.sp, col = exp1_4c6.sp@data$ID, pch = 16) 

#MCP
exp1_4c6.mcp <- mcp(exp1_4c6.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp1_4c6.mcp

```

#exp 1_4c6
```{r}
exp1_4c6.geo <- data.frame(id = exp1_4c6.sp@data$ID, 
                            exp1_4c6.sp@coords)
exp1_4c6.map <-ggmap(mybasemap) + 
  geom_point(data = exp1_4c6.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp1_4c6.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "yellow", "green")) +
  scale_fill_manual(values = c("blue", "red", "yellow", "green"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - ground - horizontal")

exp1_4c6.map

ggsave("exp1_4c6.png", plot = exp1_4c6.map, width=150, height=150, units="mm", dpi=300)

```

#exp3_4c6
```{r}
exp3_4c6.sp <- exp3_4c6[c("ID", "lat", "lng")]
coordinates(exp3_4c6.sp) <- c("lng", "lat")

#MCP
exp3_4c6.mcp <- mcp(exp3_4c6.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp3_4c6.mcp

exp3_4c6.geo <- data.frame(id = exp3_4c6.sp@data$ID, # add individual identifier
                            exp3_4c6.sp@coords)

exp3_4c6.map <-ggmap(mybasemap) + 
  geom_point(data = exp3_4c6.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp3_4c6.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "yellow", "green")) +
  scale_fill_manual(values = c("blue", "red", "yellow", "green"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - medium - horizontal")

exp3_4c6.map

ggsave("exp3_4c6.png", plot = exp3_4c6.map, width=150, height=150, units="mm", dpi=300)
```

#exp5_4c6
```{r}
exp5_4c6.sp <- exp5_4c6[c("ID", "lat", "lng")]
coordinates(exp5_4c6.sp) <- c("lng", "lat")

#MCP
exp5_4c6.mcp <- mcp(exp5_4c6.sp, percent = 100, unin = "m", unout = "m2") #all points used, no outliers excluded
exp5_4c6.mcp

exp5_4c6.geo <- data.frame(id = exp5_4c6.sp@data$ID, # add individual identifier
                            exp5_4c6.sp@coords)

mybasemap_4c6 <- get_map(location = c(lon = mean(exp5_4c6.sp@coords[,1]) , 
                                  lat = mean(exp5_4c6.sp@coords[,2])), 
                     source = "google", zoom = 17, maptype = 'satellite')

exp5_4c6.map <-ggmap(mybasemap_4c6) + 
  geom_point(data = exp5_4c6.geo, aes(x = lng, y = lat, colour = as.factor(id))) +
  geom_polygon(data = fortify(exp5_4c6.mcp), aes(x = long, y = lat, color=id, fill=id), alpha=0.2) +
  geom_point(data = nodes, aes(x = lng, y = lat), color="white", shape = 8) +
  geom_point(data = node_4C6, aes(x = lng, y = lat), color = "white", shape = 19, alpha =0.3, size=10)+
  theme(legend.position = c(0.80, 0.80)) +
  labs(x = "Longitude", y = "Latitude") +
  scale_colour_manual(name = "Tag ID",
                      values = c("blue", "red", "yellow", "green")) +
  scale_fill_manual(values = c("blue", "red", "yellow", "green"), guide=FALSE) +
  geom_text(x=-81.355, y=27.194, label = "4C6: platform 1 - medium - horizontal")

exp5_4c6.map

ggsave("exp5_4c6.png", plot = exp5_4c6.map, width=150, height=150, units="mm", dpi=300)
```